---
title: "5. Wrangle some more"
author: "Michael Aung Kyaw"
date: "(`r format(Sys.time(), '%d %B, %Y')`)"
output: github_document
---
# More data wrangling

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, message=FALSE, warning=FALSE}
library(tidyr)
library(rlang)
library(knitr)
library(dslabs)
library(dplyr)
library(magrittr)
library(ggplot2)
```

## Dataset - Gapminder
As in the example given we will use the data set *gapminder*

## Description of the dataset
```{r str}
str(gapminder)
```
The dataset gampinder contains **10454 observations** from **9 variables** which are

* **Country** - Factor variable,
* **Year** - Integer variable,
* **Infant_mortality**- Numerical variable,
* **Life_expectancy**- Numerical variable,
* **Fertility**- Numerical variable,
* **Population** - Numerical variable,
* **Continent** - Factor variable,
* **Region** - Factor variable,

## Transforming data from long to wide format

```{r long}
longgapminder <- gapminder %>%
  pivot_longer(c("life_expectancy", "fertility", ), names_to = "variable")
longgapminder %>% head() %>% kable()
```
## Manipulation fo data
```{r unite}
longgapminder <- longgapminder %>% 
  unite(cont_region, continent, region)
longgapminder %>% head() %>% kable()
```

## Transforming data from wide to long format
```{r wide}
longgapminder <- longgapminder %>% 
  separate(cont_region, into=c("continent", "region"), sep="_")
longgapminder %>% head() %>% kable()
```

## Plot 
Finally, using our original `gapminder` dataset, let's plot infant mortality against life expectancy:
```{r plot, warning=FALSE}
ggplot(gapminder, aes(infant_mortality, continent)) +
  geom_point()
```

## Source of the dataset Gampminder
**Irizarry, Rafael A., and Amy Gill. 2021. Dslabs: Data Science Labs. https://CRAN.R-project.org/package=dslabs.**